---
title: 'table1'
output:
  pdf_document:
    latex_engine: xelatex
always_allow_html: true
---

```{r}
library(knitr)
library(kableExtra)
library(readr)
library(dplyr)
library(tableone)
library(nnet)
library(tidyr)
library(broom)
library(survey)
library(forcats)
library(tibble)
```
##table 1
```{r}
Table_final <- read.csv("table1 Stratified by Food Security Status.csv")
Table_num <- read.csv("table4 numerical model.csv")
```

Table_final <- Table_final[1:39,1:6]
Table_final[is.na(Table_final)] <- ""
Table_final[Table_final == ""] <- " "
Table_final <- lapply(Table_final, function(x) gsub("%", "\\%", x, fixed = TRUE))  # Escape percent signs
Table_final <- lapply(Table_final, function(x) gsub("$", "\\$", x, fixed = TRUE))  # Escape dollar signs
Table_final <- as.data.frame(Table_final)


kable(Table_final, format = "latex", booktabs = TRUE, align = "lccccc", escape = FALSE) %>%
column_spec(1, bold = TRUE, background = "#F0FAF0") %>%
column_spec(2:6, background = "#F0FAF0") %>%
row_spec(0, bold = TRUE, background = "#E6F7E6") %>%
pack_rows("Sex (n, %)", 2, 3, background = "#FFF2CC", bold = TRUE)%>%
pack_rows("Age group (n, %)", 4, 7, background = "#FFF2CC", bold = TRUE) %>%
pack_rows("Living arrangement (n, %)", 8, 13, background = "#FFF2CC", bold = TRUE) %>%
pack_rows("Highest Education (n, %)", 14, 16, background = "#FFF2CC", bold = TRUE) %>%
pack_rows("Province Residence (n, %)", 17, 29, background = "#FFF2CC", bold = TRUE) %>%
pack_rows("Household income (n, %)", 30, 34, background = "#FFF2CC", bold = TRUE) %>%
pack_rows("Chronic Conditions (n, %)", 35, 39, background = "#FFF2CC", bold = TRUE) %>%
kable_styling(
latex_options = c("striped", "hold_position", "scale_down"), position = "left"
) %>%
add_header_above(
c("Table 1: Sociodemographic Characteristics and Chronic Conditions of Adults Aged 18 Years and Older by Household Food Security Status, 2017-2018" = 3),
escape = FALSE
)


```{r}
library(webshot) 
temp_html <- tempfile(fileext = ".html")
kable(Table_final, format = "html", booktabs = TRUE, align = "lccccc", escape = FALSE) %>%
  column_spec(1,color = "black", bold = TRUE, background = "white") %>%
  column_spec(2:6, color = "black", background = "white") %>%
  row_spec(0, color = "black", bold = TRUE, background = "#E6F7E6") %>%
  pack_rows("Sex (n, %)", 2, 3, background = "#E6F7E6",color = "black", bold = TRUE) %>%
  pack_rows("Age group (n, %)", 4, 7, background = "#E6F7E6",color = "black", bold = TRUE) %>%
  pack_rows("Living Arrangement (n, %)", 8, 13, background = "#E6F7E6", color = "black",bold = TRUE) %>%
  pack_rows("Highest Education (n, %)", 14, 16, background = "#E6F7E6", color = "black",bold = TRUE) %>%
  pack_rows("Province Residence (n, %)", 17, 29, background = "#E6F7E6", color = "black",bold = TRUE) %>%
  pack_rows("Household Income (n, %)", 30, 34, background = "#E6F7E6", color = "black",bold = TRUE) %>%
  pack_rows("Chronic Conditions (n, %)", 35, 39, background = "#E6F7E6",color = "black", bold = TRUE) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"), position = "left"
  ) %>%
  add_header_above(
    c("Table 1: Sociodemographic Characteristics and Chronic Conditions of Adults Aged 18 Years and Older by Household Food Security Status, 2017-2018" = 6),
    escape = FALSE
  ) %>%
  save_kable(temp_html)  # Save table as HTML

# Convert HTML Table to JPG
output_jpg <- "table_output.jpg"
webshot(temp_html, file = output_jpg, vwidth = 1200, vheight = 800, delay = 0.2)


```
## table 2
```{r}
Table_model1 <- read.csv("table model.csv")
Table_model1 <- Table_model1 %>%
  mutate(`p.value_adj` = ifelse(`p.value_adj` < 0.01, "<0.01", round(`p.value_adj`, 3)))  # Round others to 3 decimals
Table_model1 <- Table_model1 %>%
  rename(`Unadjusted odds ratio (95% CI)` = unadjusted, `Adjusted odds ratio (95% CI)` = adjusted, `p-value (adjusted)` = p.value_adj)

temp_html <- tempfile(fileext = ".html")
kable(Table_model1, format = "html", booktabs = TRUE, align = "lccc", escape = FALSE) %>%
  column_spec(1:4, color = "black", background = "white") %>%
  row_spec(0, color = "black", bold = TRUE, background = "white") %>%
  pack_rows("Sex (Ref Female)", 1,1, background = "#E6F7E6",color = "black", bold = TRUE) %>%
  pack_rows("Age group (Ref Age between 18 and 34)", 2, 4, background = "#E6F7E6",color = "black", bold = TRUE) %>%
  pack_rows("Living Arrangement (Ref Unattached individual living alone)", 7, 11, background = "#E6F7E6", color = "black",bold = TRUE) %>%
  pack_rows("Highest Education (Ref Less than secondary school graduation)", 5, 6, background = "#E6F7E6", color = "black",bold = TRUE) %>%
  pack_rows("Region (Ref Northern)", 12, 15, background = "#E6F7E6", color = "black",bold = TRUE) %>%
  pack_rows("Household Income (Ref No income or less than $20,000)", 16, 19, background = "#E6F7E6", color = "black",bold = TRUE) %>%
  pack_rows("Chronic Conditions (Ref No)", 20, 24, background = "#E6F7E6",color = "black", bold = TRUE) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"), position = "left"
  ) %>%
  add_header_above(
    c("Table 2: Association Between Sociodemographic Characteristics, Chronic Conditions, and Food Security Status" = 4),
    escape = FALSE
  ) %>%
  save_kable(temp_html)  # Save table as HTML

# Convert HTML Table to JPG
output_jpg <- "table_model.jpg"
webshot(temp_html, file = output_jpg, vwidth = 1200, vheight = 800, delay = 0.2)
```

## table 3
```{r}
library(webshot) 
Table_model2 <- read.csv("table model num.csv")
Table_model2 <- Table_model2 %>%
  mutate(`p.value_adj` = ifelse(`p.value_adj` < 0.01, "<0.01", round(`p.value_adj`, 3)))  # Round others to 3 decimals
Table_model2 <- Table_model2 %>%
  rename(`Unadjusted odds ratio (95% CI)` = unadjusted, `Adjusted odds ratio (95% CI)` = adjusted, `p-value (adjusted)` = p.value_adj)

temp_html <- tempfile(fileext = ".html")
kable(Table_model2, format = "html", booktabs = TRUE, align = "lccc", escape = FALSE) %>%
  column_spec(1:4, color = "black", background = "white") %>%
  row_spec(0, color = "black", bold = TRUE, background = "white") %>%
  pack_rows("Sex (Ref Female)", 1,1, background = "#E6F7E6",color = "black", bold = TRUE) %>%
  pack_rows("Age group (Ref Age between 18 and 34)", 2, 4, background = "#E6F7E6",color = "black", bold = TRUE) %>%
  pack_rows("Living Arrangement (Ref Unattached individual living alone)", 7, 11, background = "#E6F7E6", color = "black",bold = TRUE) %>%
  pack_rows("Highest Education (Ref Less than secondary school graduation)", 5, 6, background = "#E6F7E6", color = "black",bold = TRUE) %>%
  pack_rows("Region (Ref Northern)", 12, 15, background = "#E6F7E6", color = "black",bold = TRUE) %>%
  pack_rows("Household Income (Ref No income or less than $20,000)", 16, 19, background = "#E6F7E6", color = "black",bold = TRUE) %>%
  pack_rows("Chronic Conditions (Ref 0 chronic)", 20, 21, background = "#E6F7E6",color = "black", bold = TRUE) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"), position = "left"
  ) %>%
  add_header_above(
    c("Table 3: Association Between Sociodemographic Characteristics, Number of Chronic Conditions, and Food Security Status" = 4),
    escape = FALSE
  ) %>%
  save_kable(temp_html)  # Save table as HTML

# Convert HTML Table to JPG
output_jpg <- "table_model_num.jpg"
webshot(temp_html, file = output_jpg, vwidth = 1200, vheight = 800, delay = 0.2)
```